An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-29 paper/2.minbigul.tex
small fixes

We define the semantics of $put$ and $get$ as in Definitions~\ref{def:minbigulput} and \ref{def:minbigulget} respectively. Instead of using $v'$ in the $put$ direction like figures \ref{fig:eval-phead}, \ref{fig:eval-comp-phead} and \ref{fig:eval-comp-phead-2}, we just simply use notation $v$ as the updated view. The later definitions also follow this convention.

>>>>

We define the semantics of $put$ and $get$ as in Definitions~\ref{def:minbigulput} and \ref{def:minbigulget} respectively. Instead of using $v'$ in the $put$ direction like Figures~\ref{fig:eval-phead}, \ref{fig:eval-comp-phead} and \ref{fig:eval-comp-phead-2}, we just simply use notation $v$ as the updated view. The later definitions also follow this convention.

### 2019-11-29 paper/7.conclusion.tex
add labels to sections
small fixes

\section{Conclusion and Future Work}

In this paper, we focus on efficiency of composition of BX programs.
To achieve fast evaluation, we introduce two different methods using memoization.
From the experimental results of left associative BX composition programs, we know that $put_m$ is fastest method if input size is not very big and $xpg$ is fastest for other left associative programs.
This shows that if programmer choose one method based on the their BX programs and inputs, they can use efficient evaluation.

@@

We will continue our work on the following three points.
First is overcomming our limitation in $xpg$. In $xpg$, there are two limitations: only for very-well-behaved programs, restriction for $\pginline{Case}$ (shown in Section 4.1). To be a practical evlauation method, extention of the target language is needed. After extention of the language, we can evaluate more various programs for experimental results.

Second is introducing analysis about BX programs and inputs to choose the best evaluation method automatically.
Currently, programmers have to choose the evaluation method by themselves based on their BX programs and inputs. If automatic choice is possible, we can reduce programmer's burden.

Third is introducing type systems to datatype of sources and view. If we introduce this, we can avoid runtime errors like statically-typed functional languages. We need to investigate more about $construct\_dummy$, because current definition that is used in Section 6 will cause type errors.

>>>>

\section{Conclusion and Future Work} \label{sect:conclusion}

In this paper, we focus on efficiency of composition of BX programs.
To achieve fast evaluation, we introduce two different methods using memoization.
From the experimental results of left associative BX composition programs, we know that $put_m$ is fastest method if input size is not large and $xpg$ is fastest for other left associative programs.
This shows that if programmer choose one method based on the their BX programs and inputs, they can use efficient evaluation.

@@

We will continue our work on the following three points.
First is overcomming our limitation in $xpg$. In $xpg$, there are two limitations: only for very-well-behaved programs and restriction for $\pginline{Case}$ in Section~\ref{sect:pg}. To be a practical evlauation method, extention of the target language is needed. After extention of the language, we can evaluate more various programs for experimental results.

Second is introducing an automatic analysis about BX programs and inputs to choose the best evaluation method.
Currently, programmers have to choose the evaluation method by themselves based on their BX programs and inputs. If this is achieved, we can reduce programmer's burden.

Third is introducing type systems to datatype of sources and view. If we introduce this, we can avoid runtime errors like statically-typed functional languages. We need to investigate more about $construct\_dummy$, because current definition that is used in Section~\ref{sect:experiments} will cause type errors.
